Pteropod physiological analysis

### 2018-07-23 figures.Rmd
O2 back in cellular models, updated figures.Rmd

```{r effbio, fig.height = 8, fig.width = 6, eval = T}
toplo <- biomod %>% 
  filter(Model %in% c('mod3', 'mod4', 'mod17')) %>% 
  mutate(
    cvar = c('pCO2', 'Temp', 'Temp'),
    xvar = c('Fluorescence', 'Omega[ar]', 'Omega[ar]'), 
    yvar = c('LPX', 'LPX', 'SOD'), 
    legr = c('pCO[2]', 'Temp', 'Temp'),
    fct = c(0.5, 0.95, 0.95)
    ) %>% 
  mutate(
    pldat = pmap(list(Modobj, cvar, fct), function(Modobj, cvar, fct){

>>>>

```{r effbio, fig.height = 8, fig.width = 6, eval = T}
toplo <- biomod %>% 
  filter(Model %in% c('mod3', 'mod4', 'mod24')) %>% 
  mutate(
    cvar = c('pCO2', 'Temp', 'Temp'),
    xvar = c('Fluorescence', 'Omega[ar]', 'Omega[ar]'), 
    yvar = c('LPX', 'LPX', 'SOD'), 
    legr = c('pCO[2]', 'Temp', 'Temp'),
    fct = c(0.5, 0.95, 0.95)
    ) %>% 
  mutate(
    pldat = pmap(list(Modobj, cvar, fct), function(Modobj, cvar, fct){
